\parindent 0.25in
Network security has been very crucial for the software industry. Deep packet inspection (DPI) is one of the widely used approaches in enforcing network security. Due to the high volume of network traffic, it is challenging to achieve high performance for DPI in real time. In this thesis, a new DPI framework is presented that accelerates packet header checking and payload inspection on graphics processing units (GPUs). Various optimizations were applied to GPU-version packet inspection, such as thread-level and block-level packet assignment, warp divergence elimination, and memory transfer optimization using pinned memory and shared memory. The performance of the pattern-matching algorithms used for DPI was analyzed by using an assorted set of characteristics such as pipeline stalls, shared memory efficiency, warp efficiency, issue slot utilization, and cache hits. The extensive characterization of the algorithms on the GPU architecture and the performance comparison among parallel pattern-matching algorithms on both the GPU and the CPU are the unique contributions of this thesis. Among the GPU-version algorithms, the Aho-Corasick algorithm and the Wu-Manber algorithm outperformed the Rabin-Karp algorithm because the Aho-Corasick and the Wu-Manber algorithms were executed only once for multiple signatures by using the tables generated before the searching phase was begun. According to my evaluation on a NVIDIA K80 GPU, the GPU-accelerated packet processing achieved at least 60 times better performance than CPU-version processing. 