%
% Be sure to use the \url macro for URLs
%
% Also, all references in your report must be cited at least once
%
% References are alphabetized by last name of first author (or first word of title if there is no author)
%
\begin{thebibliography}{10}


\bibitem{bib1} Oosten. CUDA Thread Execution Model.
 Retrieved  November 15. 2011, from \\
\url{https://www.3dgep.com/cuda-thread-execution-model/}

\bibitem{bib2} Cyca. Maximizing Shared Memory Bandwidth on NVIDIA Kepler GPUs.
Retrieved  February 10. 2014, from \\
\url{http://acceleware.com/blog/maximizing-shared-memory-bandwidth-nvidia-kepler-gpus}

\bibitem{bib3} netgpu-framework

\bibitem{bib4} http://www.tcpdump.org/

Bondan, L., Santos, C. R., & Granville, L. Z. (2014). Management requirements for ClickOS-based Network Function Virtualization. 10th International Conference on Network and Service Management (CNSM) and Workshop. doi:10.1109/cnsm.2014.7014210  

Cabrera, J., Gosar, J., Lee, W., & Mehra, R. (2004). On the statistical distribution of processing times in network intrusion detection. 2004 43rd IEEE Conference on Decision and Control (CDC) (IEEE Cat. No.04CH37601). doi:10.1109/cdc.2004.1428609 

McKennon, J. (2013, August 6). GPU Memory Types – Performance Comparison [Blog Post]. Retrieved from https://www.microway.com/hpc-tech-tips/gpu-memory-types-performance-comparison/.

Sun, W., & Ricci, R. (2013). Fast and flexible: Parallel packet processing with GPUs and click. Paper presented at the Proceedings of the Ninth ACM/IEEE Symposium on Architectures for Networking and Communications Systems, 25-36.  doi:10.1109/ancs.2013.6665173

Vasiliadis, G., Antonatos, S., Polychronakis, M., Markatos, E. P., & Ioannidis, S. (2008). Gnort: High performance network intrusion detection using graphics processors. Paper presented at the International Workshop on Recent Advances in Intrusion Detection, 116-134. doi:10.1007/978-3-540-87403-4_7

Wuu, L., & Chen, S. (2003). Building intrusion pattern miner for snort network intrusion detection system. IEEE 37th Annual 2003 International Carnahan Conference OnSecurity Technology, 2003. Proceedings. doi:10.1109/ccst.2003.1297607 

Zha, X., & Sahni, S. (2013). GPU-to-GPU and Host-to-Host Multipattern String Matching on a GPU. IEEE Transactions on Computers, 62(6), 1156-1169. doi:10.1109/tc.2012.61


\bibitem{bib2} Vold, Erik, Will Bamberg, Kosmodrey, and Aviav. Add-on SDK Tutorials. Mozilla Developer Network. Web. Retrieved 25 Sept. 2014, from \\
\url{https://developer.mozilla.org/en-US/Add-ons/SDK/Tutorials}

\bibitem{bib3} Anderson, B., Quist, D., Neil, J., Storlie, C., \& Lane, T. (2011). Graph-based malware detection using dynamic analysis. {\it Journal in Computer Virology}, 7(4), 247-258.

\bibitem{bib3} Jetpack. MozillaWiki. Web. Retrieved 16 Dec. 2014, from \\ 
\url{https://wiki.mozilla.org/Jetpack}

\bibitem{bib4} Musale, M., Austin, T. H., \& Stamp, M. (2014). Hunting for metamorphic JavaScript malware. {\it Journal of Computer Virology and Hacking Techniques}, 1-14.

\bibitem{bib5} Ferrie, Peter. READ THE TRANSCRIPT. Virus Bulletin. (May 2013). \\
\url{https://www.virusbtn.com/pdf/magazine/2013/201305.pdf}

\bibitem{bib6} Protecting The Reputation Of Your Online Business, StopTheHacker. (Feb. 2012). \\
\url{https://www.stopthehacker.com/wp-content/uploads/2012/02/Protecting-The-Reputation-Of-Your-Online-Business4.pdf}

\bibitem{bib7} Sanger, David E., and Nicole Perlroth. Bank Hackers Steal Millions via Malware. The New York Times (14 Feb. 2015). Web. Retrieved 17 Feb. 2015, from \\
\url{http://www.nytimes.com/2015/02/15/world/bank-hackers-steal-millions-via-malware.html?_r=0}

\bibitem{bib8} Runwal, N., Low, R. M., \& Stamp, M. (2012). Opcode graph similarity and metamorphic detection. {\it Journal in Computer Virology}, 8(1-2), 37-52

\bibitem{bib9} Sophisticated Malware Forecasted to Escalate in 2015, Experts Report. (2 Feb. 2015). Retrieved 24 Feb. 2015, from \\
\url{https://www.allclearid.com/blog/sophisticated-malware-forecasted-to-escalate-in-2015-experts-report}

\bibitem{bib10} SilverRhino, Kevin G. Coleman. Cybersecurity Is No Longer an Option. C4ISR \& Networks. (12 Jan. 2015). Web. Retrieved 7 Feb. 2015, from \\
\url{http://www.c4isrnet.com/story/military-tech/blog/net-defense/2015/01/12/coleman-cybersecurity-imperative/21632093/}

\bibitem{bib11} Schiffman, Mike. A Brief History of Malware Obfuscation. Cisco Blog RSS. Cisco. (15 Feb. 2010). Web. Retrieved 18 Nov. 2014, from \\
\url{http://blogs.cisco.com/security/a_brief_history_of_malware_obfuscation_part_1_of_2 }

\bibitem{bib12} Runwal, N. (2011). Graph technique for metamorphic virus detection.

\bibitem{bib13} Mycroft Project: Search Engine Plugins - Firefox IE Chrome. Web. Retrieved 13 Feb. 2015, from \url{http://mycroftproject.com/}

\bibitem{bib14} Nachenberg, C. (1996). Understanding and managing polymorphic viruses. The Symantec Enterprise Papers, 30, 16.

\bibitem{bib15} Sharma, A., \& Sahay, S. (2014). Evolution and detection of polymorphic and metamorphic malwares: A survey. ArXiv Preprint arXiv:1406.7061,

\bibitem{bib16} Stamp, M. (2011). {\it Information security: principles and practice}. John Wiley \& Sons.

\bibitem{bib17} Creating a File on Client Side Using JavaScript. Stack Overflow. Web. Retrieved 12 Dec. 2014, from \url{http://stackoverflow.com/a/3950151}

\bibitem{bib18} Li, X., Loh, P. K., \& Tan, F. (2011). Mechanisms of polymorphic and metamorphic viruses. {\it Paper presented at the Intelligence and Security Informatics Conference (EISIC)}, 2011 European, 149-154.

\bibitem{bib19} Tanenbaum, Andrew S. Modern Operating Systems. Second ed. Englewood Cliffs, NJ: Prentice Hall, 1992. Print. Chapter 9, pp. 617-637.

\bibitem{bib20} Worthman, Ernest. The Next Big Threat: AI Malware. Semiconductor Engineering. (7 July 2014). Web. Retrieved 14 Jan. 2015, from \\
\url{http://semiengineering.com/the-next-big-threat-ai-malware/}

\bibitem{bib21} Stepan, A. E. (2005). Defeating polymorphism: Beyond emulation. {\it Paper presented at the Proceedings of the Virus Bulletin International Conference.}

\bibitem{bib22} Ször, P., \& Ferrie, P. (2001). Hunting for metamorphic. {\it Paper presented at the Virus Bulletin Conference.}

\bibitem{bib23} Desai, P., \& Stamp, M. (2010). A highly metamorphic virus generator. {\it International Journal of Multimedia Intelligence and Security}, 1(4), 402-427.

\bibitem{bib24} Orr. The Viral Darwinism of W32.Evol. VX Heaven. (Jan. 2006). Web. Retrieved 16 Oct. 2014, from \url{http://vxheaven.org/lib/vor00.html}

\bibitem{bib25} Santanam, R. (2010). Cyber security, cyber crime and cyber forensics: Applications and perspectives: Applications and perspectives IGI Global

\bibitem{bib26} Metamorphism and Self-Compilation in JavaScript. VX Heaven. (Dec. 2012). Web. Retrieved 04 Dec. 2014, from \url{http://vxheaven.org/lib/vsp45.html#c1}

\bibitem{bib27} Greg Brail, Norris Boyd, Svein Atle, and Hannes Wallnöfer. Rhino Documentation. Mozilla Developer Network. Web. Retrieved 06 Oct. 2014, from \\
\url{https://developer.mozilla.org/en-US/docs/Rhino_documentation}

\bibitem{bib28} Transcriptase JavaScript Malware source. \\
\url{http://spth.virii.lu/Transcriptase.rar}

\bibitem{bib29} Prabhu, Amar. Working of Rhino JavaScript Engine. (2 Nov. 2012). Web. Retrieved 21 Oct. 2014, from \\ 
\url{http://www.quora.com/How-does-a-JavaScript-engine-work}

\bibitem{bib30} Abstract Syntax Tree. Wikipedia. Wikimedia Foundation. Web. Retrieved 09 Jan. 2015, from \url{http://en.wikipedia.org/wiki/Abstract_syntax_tree}

\bibitem{bib31} Electrolysis/Firefox. MozillaWiki. Web. Retrieved 12 Feb. 2015, from \\
\url{https://wiki.mozilla.org/Electrolysis/Firefox}

\bibitem{bib32} Eric Shepherd, Kris Maglione, and Will Bamberg. XUL Tutorial. Mozilla Developer Network. Web. Retrieved 3 Sept. 2014, from \\
\url{https://developer.mozilla.org/en-US/Add-ons/Overlay_Extensions}

\bibitem{bib33} Will Bamberg, and Erik Vold. SDK and XUL Comparison. Mozilla Developer Network. Web. Retrieved 12 Sept. 2014, from \\
\url{https://developer.mozilla.org/en-US/Add-ons/SDK/Guides/SDK_vs_XUL}

\bibitem{bib34} List of Most Popular Websites. Wikipedia. Wikimedia Foundation. Web. Retrieved 4 Apr. 2015, from \\
\url{http://en.wikipedia.org/wiki/List_of_most_popular_websites}

\end{thebibliography}
